### 2016-09-28 notions.tex
cheers

One can also consider the orthogonal notion of \emph{privacy} for a data structure.
We specialize to the case of set-membership data structures, and
focus on sets rather than multisets. Before continuing, it will be useful to define a notion that captures the difficulty
of guessing an element in a set chosen from some distribution.
Let ${\cal D}$ be a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
min-entropy} of ${\cal D}$ is defined as
\[H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S].\]

@@

\begin{theorem}
Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
\end{theorem}
\begin{proof}
Fix a distribution ${\cal D}$ and an attacker
$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
Define an attacker $A'$ who behaves as follows: first, it samples a set $S$ according to
distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
Finally, it outputs~1 if and only if $z \in S$.

>>>>

One can also consider the orthogonal notion of \emph{privacy} for a data structure.
We specialize to the case of set-membership data structures, and
focus on sets rather than multisets. Before continuing, it will be useful to define a notion that captures the difficulty
of guessing an element in a set chosen from some distribution.
Let ${\cal D}$ be a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
min-entropy} of ${\cal D}$ is defined as
$H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S]$.

@@

\begin{theorem}\todo{rewrite}
Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
\end{theorem}
\begin{proof}
Fix a distribution ${\cal D}$ and an attacker
$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
Define an attacker $A'$ who behaves as follows: first, it samples a set $S$ according to
distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
Finally, it outputs~1 if and only if $z \in S$.

### 2016-09-28 results.tex
cheers

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$M\gets\pubaux$, $K \gets \privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets F_{K}(\langle j,x \rangle) $\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
Return 1
}
\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
  filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
  \univ \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
  algorithms for the domain-separated PRF data structure
  $\setprim_{\mathrm{ds}}$, using function family $F \colon
  \calK \times \elts \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
\label{fig:bf-and-lin}
\end{figure}

@@

\heading{Correctness. }
Fix $n,k,m \geq 0$, and fix a universe~$\univ$.  Then $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).  We define~$\setprim_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.  Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives).
The proof appears in Appendix~\ref{sec:thm3_fp}.

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

@@

\begin{theorem}\label{thm3}\label{thm:bf-ow} \todo{Finish typesetting.  Result is on chalkboard.}
Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
\]
\end{theorem}

\subsection{Privacy of Secretly Keyed Canonical Data Structures}
Here we prove a result that can be used to show that a large class of ``canonical''
data structures are semantically secure, with respect to leakage of the size of the set.
\jnote{It would not be too hard to generalize this to arbitrary data structures over
arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
depends only on ${\sf leak}$.}

We first define what we mean by ``canonical.''

@@

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows: 
(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$. 
%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
%\jnote{Not sure how general to make the above. Need to verify that it is general enough
%to prove security of all the constructions we care about.}
\tsnote{Point out an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
with respect to leakage function ${\sf leak}(S) = |S|$.
\tsnote{We have a mixture of styles of theorem statements, resource-parameterized statements vs.\ ``verbose'' concrete statements.  We
  need to make things uniform.}
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes a
set $S^*=\{e_1, \ldots, e_n\}$. In then computes:
(1) $s_1, \ldots, s_t \getsr \Rep_1(S^*)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and
finally returns $\pubaux$.

@@

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}. For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

@@

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
if $\privaux \neq \emptystring$ then\\
\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
else\\
\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
$x' \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H_{K_j}(x)$\\
\nudge $x' \gets x' \xor M[h_j]$\\
if $x' =x $ then Return 1\\
Return 0
}
\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
 \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon
  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}

>>>>

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$M\gets\pubaux$, $K \gets \privaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets F_{K}(\langle j,x \rangle) $\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
Return 1
}
\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
  filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
  \elts \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
  algorithms for the domain-separated PRF data structure
  $\setprim_{\mathrm{ds}}$, using function family $F \colon
  \calK \times \elts \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
\label{fig:bf-and-lin}
\end{figure}

@@

\heading{Correctness. }
Fix $n,k,m \geq 0$, and fix a set $\elts$.  Then the classical Bloom filter set-membership data structure $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).  We define~$\setprim_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.  Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives).
The proof appears in Appendix~\ref{sec:thm3_fp}.

\begin{theorem}\label{thm3}\label{thm:bf-correctness}
Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter set-membership data structure. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

@@

\begin{theorem}\label{thm3}\label{thm:bf-ow} 
Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
\]
\end{theorem}
\todo{Typeset simple proof.  Result is on chalkboard.}

\subsection{Privacy of Secretly-Keyed ``Canonical'' Data Structures}
Here we prove a result that can be used to show that a large class of canonical
data structures are SS-secure, with respect to leakage of the size of the set.
\jnote{It would not be too hard to generalize this to arbitrary data structures over
arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
depends only on ${\sf leak}$.}
We first define what we mean by ``canonical.''

@@

\begin{definition}
A data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows: 
(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$. 
%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
\end{itemize}
We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
%\jnote{Not sure how general to make the above. Need to verify that it is general enough
%to prove security of all the constructions we care about.}
\tsnote{Point out an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

\begin{theorem}\todo{Rewrite to match old DS-PRF proof}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$ has canonical representation
$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
with respect to leakage function ${\sf leak}(S) = |S|$.
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes a
set $S^*=\{e_1, \ldots, e_n\}$. In then computes:
(1) $s_1, \ldots, s_t \getsr \Rep_1(S^*)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and
finally returns $\pubaux$.

@@

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}. For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

@@

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
if $\privaux \neq \emptystring$ then\\
\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
else\\
\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
$x' \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H_{K_j}(x)$\\
\nudge $x' \gets x' \xor M[h_j]$\\
if $x' =x $ then Return 1\\
Return 0
}
\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
 \elts \to [m]$. The query set is $\calQ=\{\qry_x\colon
  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}
